\section{Tuesday, January 31st: In-Class Team Brainstorm}
\subsection{Logistics: Assignments due!}
\begin{itemize}
    \item Team Brainstorm
    \begin{itemize}
        \item Aim for \~50 visual ideas!
    \end{itemize}
    \item Outside of class:
    \begin{itemize}
        \item Select initial course idea
        \item Target specific users (not students)
        \item Be creative -- you app should not be found in the app store!
    \end{itemize}
    \item Team Collaborative Plan
    \begin{itemize}
        \item Meet as a team
        \item Figure out team's strength/weaknesses
        \item Figure out how/when you'll meet
    \end{itemize}
    \item Individual Programming Assignment 1: Electric Time
    \begin{itemize}
        \item Simple web app
        \item Deploy, test, debug app locally
        \item Document \& showcase design + interactive features
        \item will be a Personal Transportation Conversion app
        \item Section (More HTML + JS) will help with starting this!
    \end{itemize}
    \item Thursday's Lecture: Conceptual Models + associated Reading Response
\end{itemize}

\subsection{Team Project}
\begin{shaded}
Be ambitious, yet realistic.
\end{shaded}
\subsubsection{Intelligent User Interfaces}
Example: Audio Fingerprinting a la Shazam.
\begin{itemize}
    \item Text-to-speech and Speech-to-text
    \item Translation
    \item Optical Character Recognition
    \item Image labeling, face, logo and landmark detection
    \item Image generation
    \item Classification and prediction using your own data
    \item Dialog systems (chatbots)
\end{itemize}
Example: Automatic Data Entry

Example: Automatic Text Translation

\subsubsection{Designing Inclusive Technologies}
\begin{shaded}
Abilities change over the course of our lives
\end{shaded}
Also recall that impairments can be:
\begin{itemize}
    \item Permanent (i.e. losing an arm)
    \item Temporary (i.e. arm injury)
    \item Situational (i.e. new parent with baby in one arm)
\end{itemize}

\subsection{In-Class Team Brainstorm: Meeting time!}
For the rest of the class please think of at least 50 app ideas that serve an underrepresented community.

The first group to finish will win free cookies!
\begin{shaded}
The winners were Group 8 consisting of Henry La, Karissa Wong, Priscila Figueroa, Rae Xin, and Rahul Shah.
\end{shaded}
