\section{Thursday, February 2nd}
\subsection{Contextual Inquiry, Conceptual Models 1}
\subsubsection{Case Study: Apple Watch}
You can have a modular home screen or one like traditional watches.

\subsubsection{Case Study: Calculators}
The 1990 HP-48SX calculator had an android emulator which mimicked it completely with overloaded buttons for easy familiarity at the cost of small hard to push buttons due to the touchscreen.

\subsection{Reminder: Assignments}
Tue Feb 7:
\begin{itemize}
\item Reading Response
\end{itemize}

Thu Feb 9:
\begin{itemize}
\item Team Collaborative Plan
\item Team Brainstorm
\end{itemize}

Mon Feb 13:
\begin{itemize}
\item Programming Assignment 1 – Electric Time
\end{itemize}

\subsection{Contextual Inquiry}
\subsubsection{Goals}
\begin{itemize}
    \item Go to where the customer works
    \item See what they do
    \item Talk to them about what they do
\end{itemize}
This gets you out of your perspective and see their tasks the way they do -- a mix between observing and interviewing.

\subsubsection{Context}
You want details not abstractions -- you want to be able to see their work live, in action.

When people are removed from their work environment they can only tell not show.

\myparagraph{Why not just interview folks?}
Folks may be used to inefficiencies and just accept things as ``that's just how things are done''

\subsubsection{Affordances}
The term affordance refers to the 
relationship between properties of a 
physical object and capabilities of a 
person, that determine how the object 
could be used.  

\subsubsection{Signifiers}
Signifiers help people figure out the 
affordances of objects without labels 
or instructions

\myparagraph{Case Study: Doors}
Q: How to make clear whether you push vs pull to open the door?

A: Make it so that there is only one clear way to do the intended action (i.e. no door handle implies push whereas

\subsubsection{Universal Signals}
Red means stop;\\
Green means go.

\subsubsection{Incorrect signifiers}
\begin{important}
Be careful: Signifiers may suggest affordances that do not exist.
\end{important}
