% lec 12
\section{Thursday, February 23th: Midterm 1 Review}
\subsection{Logistics}
The quiz will be on bcourses under the ``Quizzes'' section. We will post a clarification form and have times on when we will monitor Ed posted.

\subsection{Composition}
Use grid systems -- what most web apps use!

Note that a text can be multiple grid cells but you mentally think of it wrt multiples of grid cells with whitespace in between.

\subsection{Alignment}
Every item on a screen has a relationship to the 
other items. Elements that are almost collinear 
should be aligned. 

Left, right and both-justified alignments create strong 
boundaries around a piece of text -- do not center allign text as you do not have an easy side border to read in a deterministic non-causal manner. 

Its best to stick with one kind of justification within 
a page.

\subsection{Common Mistakes}
\begin{important}
\begin{itemize}
    \item Arbitrary component positions and dimensions
    \item Random window sizes and layouts
    \item Unrelated icon sizes and imagery
    \item Poor alignment
\end{itemize}
\end{important}

\subsection{Summary}
What are the 3 stages of design cycle?

The Design Cycle is not everything.

As you go through the design cycle, you consider lots (>50 in brainstorming) but you end up shipping 1 product (divergent $\to$ convergent phases).

\subsection{Review}
\begin{shaded}
This has been added to the previous sections, as is relevant.
\end{shaded}

Good exam questions: 
\begin{itemize}
    \item If I tell you an object, tell me what its affordances are?

    \item Give an example of a mode that wasn't mentioned in lecture slides.

    \item Give an example of a task that follows a power law (i.e. typing).
\end{itemize}
